\documentclass[10pt,onecolumn]{article}

\usepackage{amsmath}
\usepackage[top=1cm, bottom=1cm, right=1cm, left=1cm]{geometry}
\usepackage{graphics}
\usepackage{adjustbox}

\newcommand{\break}{\\ \\}

\title{Nuclear Physics \\ \large Journal of Study}
\author{Amir H. Ebrahimnezhad}


\begin{document}
\maketitle
\tableofcontents

\section{Introduction}
The fundamental constituents of matter was always a question for the great minds of each era. From the greek philosophers that tried to explain the matter using four fundamental ones, to the recent years that the standard model tries to explain what are the interactions between the fundamental particles that form up the world around us.
\break
The physicists have found smaller and smaller particles that make up the matter around us. The atom, the substructure of the atom, electrons, nuclei, The substructure of nuclei, protons and neutrons, and the substructure of protons and neutrons which are quarks. 
\break
The two fundamental types of building blocks are the \texit{leptons}, which include the electron and the neutrino, and the quarks. In the scattering experiments, these were found to be smaller than $10^{-18}$m. They are possibly point-like particles.  For comparison, protons are as large as $10^{-15}$m. 

\subsection{Fundamental Interactions}
By the end of 19th-century there were two known forces in the world. Gravity and electromagnetism, the first described all the observed motions in the night sky and the macroscopic objects around, while the latter explained the interactions causing chemical reactions. With the development of nuclear physics two new forces were introduced. The reason behind the absence of these forces was the short-range nature of them.

Thus the four fundamental interactions on which all physical interactions are based upon are:
\begin{itemize}
     \item Gravitation
     \item Electromagnetic interaction
     \item Weak interaction
     \item Strong interaction
\end{itemize}

According the today's conceptions, we tend to assing a mediator for each interaction. Thus except from gravitation which is still a mistery in fundamental physics we have:

\begin{itemize}
     \item Weak interactions mediators are \textbf{W-Boson} and \textbf{Z-Boson}.
     \item Strong interactions mediator is \textbf{Gluon}
     \item Electromagnetic interactions mediatos is the photon.
\end{itemize}







\end{document}